---
title: "temp"
subtitle: 'Preliminary draft'
author: "Michael Gurkov"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
output:
  rmarkdown::pdf_document:
    number_sections: true
abstract: "Text for abstract"
bibliography: ipo_long_run.bib
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,echo = FALSE,
  message = FALSE,warning = FALSE,
  comment = "#>"
)
```


```{r get_bib_filepath, include = FALSE}

file.copy(paste0(Sys.getenv("USERPROFILE"),
                 "\\OneDrive - Bank Of Israel",
                 "\\References\\ipo_long_run.bib"),
          "ipo_long_run.bib")

```

<!-- import_data -->


```{r load_libraries}

library(tidyverse)

library(xts)

library(lubridate)

library(stargazer)

devtools::load_all()

# library(MiscImport)

```


```{r import_ta_125}

ta_125 = read_csv(paste0(Sys.getenv("USERPROFILE"),
                         "\\OneDrive - Bank Of Israel\\Data",
                         "\\TASE liquidity\\michael files",
                         "\\TA125.csv"),
                  show_col_types = FALSE) %>% 
  mutate(date = dmy(date))

```

```{r import_tase_sector}

tase_sector_df = read_csv(paste0(Sys.getenv("USERPROFILE"),
                                 "\\OneDrive - Bank Of Israel\\Data",
                                 "\\TASE liquidity\\michael files",
                                 "\\tase_sector_classification.csv"),
                          show_col_types = FALSE) %>% 
  select(-comp_name_hebrew) %>% 
  filter(!tase_sector == "#N/A") %>% 
  mutate(date = as.yearmon(date, format = "%d/%m/%Y")) %>% 
  mutate(across(-date, as.character)) %>% 
  select(-tase_sub_sector)

```

```{r import_market_df, cache=TRUE}

market_df_filepath = paste0(Sys.getenv("USERPROFILE"),
                                "\\OneDrive - Bank Of Israel\\Data",
                                "\\TASE liquidity\\Rdata files",
                                "\\market_data_2022-12-12.rds")

market_df = import_boi_market_data(market_df_filepath) %>% 
  calculate_adjusted_price() %>% 
  filter(date <= max(ta_125$date))

rm(market_df_filepath)

```

```{r import_ipo_list}

stocks_ipo = read_csv(paste0(Sys.getenv("USERPROFILE"),
                             "\\OneDrive - Bank Of Israel",
                             "\\Data\\TASE liquidity",
                             "\\michael files\\stocks_ipo.csv"),
                      show_col_types = FALSE) %>% 
  mutate(tase_id = as.character(tase_id))

stocks_ipo = stocks_ipo %>% 
  mutate(tase_id = recode(tase_id,
                          `456` = "259"))

cpi_df = read_csv(paste0(Sys.getenv("USERPROFILE"),
                         "\\OneDrive - Bank Of Israel\\Data",
                         "\\BoI\\monetary_data\\cpi.csv"),
                  show_col_types = FALSE,
                  skip = 15,col_names = c("date","cpi")) %>% 
  mutate(date = dmy(date)) %>% 
  group_by(year = year(date)) %>% 
  summarise(cpi = mean(cpi), .groups = "drop") %>% 
  filter(year >= 2000) %>% 
  mutate(cpi = cpi / cpi[year == 2000])


stocks_ipo = stocks_ipo %>% 
  left_join(cpi_df, by = "year") %>% 
  mutate(real_domestic_issue = domestic_issue / cpi) %>% 
  select(-cpi)


# ipo_trade_dur_df = market_df %>% 
#   group_by(tase_id, sec_id) %>% 
#   summarise(tibble(first_trade_year = year(min(date)),
#                    trade_years = (max(date) - min(date)) %/% dyears(1)),
#             .groups = "drop")
# 
# stocks_ipo = stocks_ipo %>% 
#   left_join(ipo_trade_dur_df, by = "tase_id") %>% 
#   arrange(tase_id) %>% 
#   filter(!is.na(trade_years))
# 
# 
# 
# num_ipo = stocks_ipo %>% 
#   count(tase_id, sort = TRUE)
# 
# 
# stocks_ipo = stocks_ipo %>% 
#   inner_join(num_ipo %>% 
#                filter(n == 1) %>% 
#                select(tase_id), by = "tase_id")
# 
# rm(ipo_trade_dur_df)

```


<!-- Matching by sector -->


```{r match_control_comps}


ipo_control_match_df = match_control_group(market_df,
                                           tase_sector_df,stocks_ipo)

rm(tase_sector_df)

```

```{r price_df}

price_df = make_price_df(market_df,ipo_control_match_df,ta_125)


```

```{r cumulative_returns}

ret_df = calculate_return_df(price_df)

cum_ret_df = ret_df %>% 
  calculate_cum_return()

```

```{r holding_returns, eval=FALSE}

hold_ret = calculate_holding_return(ret_df)

hold_ret = hold_ret %>% 
  mutate(tase_id = str_extract(id,"^[0-9]+")) %>% 
  left_join(stocks_ipo %>% 
              select(tase_id, tase_sector), by = "tase_id")

hold_ret = hold_ret %>% 
  left_join(stocks_ipo %>%
              select(tase_id, year), by = "tase_id")

hold_ret = hold_ret %>% 
  select(-tase_id)

```


```{r clean_up, eval=FALSE}

rm(ipo_control_match_df,ta_125,ret_df, market_df)

```


\section{Data}

```{r ipo_by_year, results='asis'}

stocks_ipo %>% 
  select(year, real_domestic_issue) %>% 
  group_by(year) %>% 
  summarise(num_ipo = length(real_domestic_issue),
            real_total_issue = sum(real_domestic_issue),
            .groups = "drop") %>% 
  mutate(real_total_issue = round(real_total_issue,2)) %>% 
  rename(Year = year, `Number of IPO's` = num_ipo,
         `Real proceeds` = real_total_issue) %>% 
  as_data_frame() %>% 
  stargazer(summary = FALSE,header = FALSE, rownames = FALSE,
            title = "Distribution of IPO's by year")

```


```{r ipo_by_sector, results='asis'}

stocks_ipo %>% 
  select(tase_sector, real_domestic_issue) %>% 
  group_by(tase_sector) %>% 
  summarise(num_ipo = length(real_domestic_issue),
            real_total_issue = sum(real_domestic_issue),
            .groups = "drop") %>% 
  mutate(real_total_issue = round(real_total_issue,2)) %>% 
  rename(Sector = tase_sector, `Number of IPO's` = num_ipo,
         `Real proceeds` = real_total_issue) %>% 
  as_data_frame() %>% 
  stargazer(summary = FALSE,header = FALSE, rownames = FALSE,
            title = "Distribution of IPO's by sector")

```


```{r plot_cum_ret}

cum_ret_df %>% 
  ggplot(aes(month, value, color = adjustment_type)) +
  geom_line() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_y_continuous(labels = scales::percent_format()) +
  xlab("Months since IPO") + ylab(NULL) +
  ggtitle("Cumulative returns since IPO") +
  theme(legend.title = element_blank())



```



\section{Results}


<!-- check whether most of the firms dropped? -->

<!-- plot attrition by years -->


```{r plot_hold_ret, eval=FALSE}

q_vec = seq(0.05,0.95, 0.05)

hold_ret %>% 
  group_by(adjustment_type) %>% 
  summarise(tibble(returns = quantile(hold_ret,q_vec,na.rm = TRUE),
                   quantiles = q_vec), .groups = "drop") %>% 
  ggplot(aes(as.character(quantiles), returns, fill = adjustment_type)) + 
  geom_col(position = "dodge") + 
  scale_y_continuous(labels = scales::percent_format()) + 
  xlab("Quantile") + ylab(NULL) + ggtitle("3 year holding returns")

rm(q_vec)

```


\subsection {Aftermarket performance by sector}


```{r plot_returns_by_sector, eval=FALSE}

hold_ret %>%
  filter(complete.cases(.)) %>% 
  group_by(tase_sector, adjustment_type) %>% 
  summarise(avg_ret = mean(hold_ret), .groups = "drop") %>% 
  ggplot(aes(x = avg_ret,
             y = tidytext::reorder_within(tase_sector,avg_ret,
                                          adjustment_type))) + 
  geom_col(aes(fill = (avg_ret >= 0)),position = "dodge", width = 0.5,
           show.legend = FALSE) + 
  geom_vline(xintercept = 0, linetype = "dashed") + 
  tidytext::scale_y_reordered() + 
  scale_x_continuous(labels = scales::percent_format()) + 
  facet_wrap(~adjustment_type, scales = "free") + 
  xlab(NULL) + ylab(NULL)


hold_ret %>% 
  filter(tase_sector == "fin_services") %>% 
  select(id) %>% 
  distinct()



```


\subsection {Aftermarket performance by year of Issuance}

```{r plot_returns_by_year, eval=FALSE}


hold_ret %>%
  filter(complete.cases(.)) %>% 
  group_by(year, adjustment_type) %>% 
  summarise(avg_ret = mean(hold_ret), .groups = "drop") %>% 
  ggplot(aes(x = year, y = avg_ret, fill = adjustment_type)) + 
  geom_col(position = "dodge", width = 0.5) + 
  scale_fill_viridis_d() + 
  scale_y_continuous(labels = scales::percent_format()) + 
  xlab(NULL) + ylab(NULL) + ggtitle("Holding returns by year")



```


\subsection{Regression results}

```{r, eval=FALSE}



reg_df = hold_ret %>% 
  filter(!adjustment_type == "control_ret") %>% 
  pivot_wider(names_from = adjustment_type, values_from = "hold_ret") %>% 
  mutate(index_ret = close_ret - index_ret) %>% 
  left_join(stocks_ipo %>% 
              count(year,name = "vol"), by = "year") %>% 
  select(-c(id,year))

summary(lm("close_ret ~ index_ret + vol + tase_sector", data = reg_df))

```


\section{Robustness}


```{r cumulative_returns_from_trading_start, eval=FALSE}

cum_ret_df_robust = market_df %>% 
  select(tase_id, sec_id,date, close = close_adjusted) %>% 
  inner_join(stocks_ipo %>% 
               select(tase_id),by = "tase_id") %>% 
  left_join(ta_125 %>% 
              rename(index = ta_125), by = "date") %>% 
  group_by(tase_id, sec_id) %>% 
  arrange(date) %>% 
  mutate(month = as.numeric(date - date[1]) %/% 22) %>% 
  group_by(tase_id, sec_id, month) %>% 
  summarise(across(c("close","index"),~mean(., na.rm = TRUE)),
            .groups = "drop") 

cum_ret_df_robust = cum_ret_df_robust %>% 
  group_by(tase_id, sec_id) %>% 
  mutate(across(c("close","index"),
                .fns = list(log_ret = ~log(.) - log(.[1]),
                            simple_ret = ~ . /.[1] - 1))) %>% 
  ungroup() %>% 
  select(-c("close","index"))

cum_ret_df_robust = cum_ret_df_robust  %>% 
  pivot_longer(contains("ret"),names_to = "category") %>% 
   extract(category, into = c("source","ret_type"),
          regex = "^([^_]*)_(.*)") %>% 
  pivot_wider(names_from = source) %>% 
  mutate(index_adj = close - index) %>% 
  select(-index) %>% 
  pivot_longer(c("close","index_adj"),
               names_to = "adjustment_type")


```

 * \textcolor{red}{calculate abnormal return using CAPM residuals}


\newpage

\section{References}

<div id="refs"></div>

\section{Appendix}

The return measures used in the paper are:

\begin{itemize}
  \item
  Cumulative average adjusted returns (CAR)
  \item
  Buy and hold abnormal returns (BHAR)
  \item
  Calendar time abnormal returns (CTAR)
\end{itemize}


\subsubsection{CAR}

The cumulative return is calculated on a monthly basis where months are defined as successive 21-trading-day periods relative to the IPO date. Thus, month 1 consists of event days 1-21, month 2 consists of event days 22-43, etc.

Benchmark adjusted returns are calculated as a difference between monthly raw
return and the monthly return of benchmark index.
Thus, the benchmark return is defined as:

\begin{equation*}
  ar_{i,t} = r_{i,t} - r_{benchmark,t}
\end{equation*}

and the adjusted return for the portfolio of N stocks is the simple average
of the adjusted returns of the individual stocks.

\begin{equation*}
  AR_{t} = \frac{1}{N} \sum_{i = 1}^{N}ar_{i,t}
\end{equation*}


The cumulative benchmark-adjusted aftermarket performance from event
month q to event month s is the summation of the average benchmark-adjusted returns:

\begin{equation*}
  CAR_{q,s} = \sum_{t = q}^{s}AR_{t}
\end{equation*}

\subsubsection{BHAR}

The buy-and-hold abnormal return (BHAR) is defined as follows:

\begin{equation*}
  BHAR_{i,T} = \left[\prod_{t = 1}^{T}(1 + r_{i,t}) - 1\right] - \left[\prod_{t = 1}^{T}(1 + r_{m,t}) - 1\right]
\end{equation*}

Where:
$r_{i,t}$ - the return of firm $i$ in month $t$

$r_{m,t}$ - the return of corresponding benchmark in month $t$
