---
title: "temp"
subtitle: 'Preliminary draft'
author: "Michael Gurkov"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
output:
  rmarkdown::pdf_document:
    number_sections: true
abstract: "Text for abstract"
bibliography: ipo_long_run.bib
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,echo = FALSE,
  message = FALSE,warning = FALSE,
  comment = "#>"
)
```

```{r params, include=FALSE}

eval_mode = FALSE

```



```{r get_bib_filepath, include = FALSE}

file.copy(paste0(Sys.getenv("USERPROFILE"),
                 "\\OneDrive - Bank Of Israel",
                 "\\References\\ipo_long_run.bib"),
          "ipo_long_run.bib")

```


```{r child="import_data.rmd", eval=eval_mode}

```


\section{Literature review}

```{r child="lit_review.rmd"}

```


\section{Descriptive stats}

```{r child="descriptive_stats.rmd", eval=eval_mode}

```


\section{Analysis}

```{r child="analysis.rmd", eval=eval_mode}

```



\section{Methodology}

I use three measures in order to evaluate the long run performance of the IPOs:
cumulative abnormal returns (CARs), buy-and-hold abnormal returns (BHARs) and calendar-time abnormal return (CTARs). I measure the after market period in two time points : 36 months and 60 months after the first trading day (so that return is measured from first closing price) where month is defined as 21 trading days period. The excessive returns are calculated as benchmark adjusted returns where the benchmarks are: (1) TASE TA 125 market index and (2) control firms matched by sector and size.


\section{Results}


\section{References}

<div id="refs"></div>

\section{Appendix}

