---
title: "Work outline"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```


```{r Set_parameters}

filepath = paste0("C:\\Users\\internet\\Documents\\Data\\TASE\\",
                     "TASE_Liquidity\\quarterly regression updated.csv")

```


```{r Import_data}

library(tidyverse)

library(xts)

library(stargazer)

df = read.csv(filepath)

delisted_firms = unique(df$MSP_HVR[df$delisted == 1])

df = df %>% 
  mutate(DATE = as.yearqtr(DATE, format = "%d/%m/%Y")) %>% 
  group_by(MSP_HVR) %>% 
  mutate(delisted = cumsum(delisted))



```

\section{Introduction}

The purpose of the work is to identify the reasons
of firm's delistings from trade. The method is a logit regression that evaluates firm's characteristics in a sample
that consists of delisted firms and matched trading firms.

\section{Empirical specification}

\begin{equation}
Pr(Delisting) = \alpha  + 
\beta_{1} Leverage +
\beta_{2} MB + 
\beta_{3} ROA + 
\beta_{4} Insider \hspace{5pt} ownership
\end{equation}


\section{Descriptive Stats}

The sample consists of `r length(unique(df$MSP_HVR))` firms,
out of which `r length(unique(df$MSP_HVR[df$delisted == 1]))` delisted from trading. The sample period is `r paste(range(df$DATE, na.rm = TRUE), collapse = "-")`

```{r desc_stat, eval=FALSE}

stat_table = df %>% 
  ungroup() %>% 
  select(delisted,erh_shuk,minuf_aroh) %>% 
  group_by(delisted) %>% 
  summarise_all(mean, na.rm = TRUE) %>% 
  filter(complete.cases(.)) %>% 
  t() %>% 
  as.data.frame() %>% 
  setNames(c("Control","Delisted")) %>% 
  slice(-1)

```


```{r output_summary, results="asis"}

stargazer(df %>% 
            ungroup() %>% 
            select(delisted,erh_shuk,minuf_aroh),
          header = FALSE,
          omit.summary.stat = c("p25","p75","n"))

```


\subsection{Raw variables}
The data file has a set of id variables that identify the company and its
industry. There are financial variables that specify the company's market value,
its turnover, assets, profit (net and gross), equity, liabilities and leverage.
The are indicators variables that identify dual listing, recession periods, IPO
year (and date). There are dates of the start and end of trading.

\subsection{Calculated variables}

Amihud's illiquiduty measure, size classification of the companies according to
market value : core (30 largest comps), mid (31-100 largest) and the rest.
Hirshman-Herfindal index and ownership variables: inside ownership and free
float. There are trading period variables (duration)