
```{r load_libraries}

library(tidyverse)

library(xts)

library(lubridate)

devtools::load_all()

# library(MiscImport)

```


```{r import_ipo_list}

stocks_ipo = read_csv(paste0(Sys.getenv("USERPROFILE"),
                             "\\OneDrive - Bank Of Israel",
                             "\\Data\\TASE liquidity",
                             "\\michael files\\stocks_ipo.csv"),
                      show_col_types = FALSE) %>% 
  mutate(tase_id = as.character(tase_id))


```

```{r import_ta_125}

ta_125 = read_csv(paste0(Sys.getenv("USERPROFILE"),
                         "\\OneDrive - Bank Of Israel\\Data",
                         "\\TASE liquidity\\michael files",
                         "\\TA125.csv"), show_col_types = FALSE)

```

```{r import_market_df}

# 
# market_file_path = paste0(Sys.getenv("USERPROFILE"),
#                           "\\OneDrive - Bank Of Israel\\Data",
#                           "\\TASE liquidity\\Rdata files",
#                           "\\market_data_2022-11-15.rds")
# 
# 
# market_df  = import_boi_market_data(market_file_path) %>% 
#   filter(!is.na(close))
# 
# market_df %>% 
#   write_rds(paste0(Sys.getenv("USERPROFILE"),
#                           "\\OneDrive - Bank Of Israel\\Data",
#                           "\\TASE liquidity\\Rdata files",
#                           "\\working_data\\market_df.rds"))
# 
# rm(market_file_path)


market_df = read_rds(paste0(Sys.getenv("USERPROFILE"),
                          "\\OneDrive - Bank Of Israel\\Data",
                          "\\TASE liquidity\\Rdata files",
                          "\\working_data\\market_df.rds"))




```


```{r cumulative_returns}

cum_ret_df = market_df %>% 
  select(tase_id, sec_id,date, close) %>% 
  inner_join(stocks_ipo %>% 
               select(tase_id)) %>% 
  group_by(tase_id, sec_id, date = as.yearmon(date)) %>% 
  summarise(close = mean(close, na.rm = TRUE), .groups = "drop") %>% 
  group_by(tase_id, sec_id) %>% 
  arrange(date) %>% 
  mutate(trade_periods = (date - date[1])) %>% 
  mutate(trade_periods = round(trade_periods,4)) %>%
  mutate(cum_ret = log(close) - log(close[1])) %>% 
  # mutate(avg_ret = cum_ret / trade_periods) %>% 
  ungroup()


```


# Desc stats

```{r clasify_num_ipo}

num_ipo = stocks_ipo %>% 
  count(tase_id, sort = TRUE)

```


The sample contains `r nrow(num_ipo)` companies that performed
initial public offering on TASE. `r sum(num_ipo$n > 1)` of the
companies exited the market and came back later again performing an
IPO. For now this companies are excluded from the analysis.

```{r exclude_returning_comps}


cum_ret_df = cum_ret_df %>% 
  anti_join(num_ipo %>% 
              filter(n > 1) %>% 
              select(tase_id), by = "tase_id")

```


## Attrition

```{r plot_attrition}

cum_ret_df %>% 
  mutate(years = round(trade_periods / 12,2)) %>% 
  count(years,name = "num_of_comps") %>% 
  ggplot(aes(years,num_of_comps)) + 
  geom_line() + 
  xlab(NULL) + ylab(NULL) + 
  ggtitle("Number of trading IPO companies (years since IPO)")



```


```{r ipo_trade_duration}

ipo_trade_dur_df = cum_ret_df %>% 
  group_by(tase_id, sec_id) %>% 
  summarise(trade_len = max(date) - min(date),
            .groups = "drop") %>% 
  mutate(trade_len = round(trade_len,2)) %>% 
  group_by(tase_id) %>% 
  summarise(trade_len = mean(trade_len, na.rm = TRUE))


stocks_ipo %>% 
  select(-comp_name_heb) %>% 
  inner_join(ipo_trade_dur_df, by = "tase_id") %>% 
  filter(year == 2007)
  ggplot(aes(x = as.character(year), y = trade_len)) + 
  geom_boxplot() + 
  xlab(NULL) + ylab(NULL)


  
  

```


IPO companies exit the market quite quickly. The mean trading
periond is 'r round(mean(ipo_trade_dur_df$trade_len),2' years
median trading perions is
'r round(median(ipo_trade_dur_df$trade_len),2)' years.

# Long run performance

In order to asses the long run performance of IPO's I calculate the buy and hold return 


```{r ,eval=FALSE}

volatile_comps = cum_ret_df %>% 
  group_by(tase_id, sec_id) %>% 
  summarise(ret_sd = sd(cum_ret, na.rm = TRUE), .groups = "drop") %>% 
  arrange(desc(ret_sd))


market_df %>% 
  inner_join(volatile_comps %>% 
               slice(40:45) %>% 
               select(tase_id), by = "tase_id") %>% 
  group_by(tase_id) %>% 
  arrange(date) %>% 
  # mutate(close = close / close[1]) %>% 
  # ungroup() %>% 
  ggplot(aes(date, close)) + 
  geom_line() + 
  facet_wrap(~tase_id, scales = "free") +
  xlab(NULL) + ylab(NULL)



market_df %>% 
  filter(tase_id == 1803) %>% 
  arrange(date) %>% 
  select(date, close) %>% 
  head()


```


```{r plot_cum_ret}

cum_ret_df  %>% 
  filter(trade_periods <= 10) %>%
  group_by(trade_periods) %>% 
  summarise(across(cum_ret,.fns = list(mean = mean,
                                   median = median),
                   .names = "{.col}_{.fn}")) %>% 
  pivot_longer(-trade_periods, names_to = "metric") %>% 
  mutate(metric = str_remove(metric,"ret_")) %>% 
  ggplot(aes(trade_periods, value, color = metric)) + 
  geom_line() + 
  scale_y_continuous(labels = scales::percent_format()) + 
  scale_x_continuous(breaks = seq(0,10,2)) + 
  xlab("Years since IPO") + ylab(NULL) + 
  ggtitle("Cumulative returns since IPO")



```


```{r plot_ipo_long_run_performance_by_sector}

library(tidytext)


ret_df %>% 
  select(-year) %>%
  pivot_longer(-c(tase_id,sec_id,tase_sector, horizon),
               names_to = "adjustment") %>% 
  group_by(horizon,tase_sector,adjustment) %>% 
  summarise(avg = mean(value, na.rm = TRUE),
            med = median(value, na.rm = TRUE),
            .groups = "drop") %>% 
  filter(adjustment == "sec_ret_adj") %>%
  select(-adjustment) %>% 
  pivot_longer(-c(tase_sector, horizon)) %>% 
  ggplot(aes(x = value,
             y = reorder_within(tase_sector, value, horizon)),
             fill = name) + 
  geom_col(position = "dodge") + 
  facet_wrap(~horizon, scales = "free") + 
  scale_y_reordered() +
  scale_x_continuous(labels = scales::percent_format()) +
  xlab(NULL) + ylab(NULL)
  


# ret_df %>% 
#   select(contains("tase"), contains("ret")) %>%
#   pivot_longer(-c(tase_id,tase_sector),
#                names_to = "adjustment") %>% 
#   group_by(adjustment, tase_sector) %>% 
#   summarise(avg = mean(value),
#             .groups = "drop") %>% 
#   pivot_wider(names_from = adjustment, values_from = avg) %>% 
  # write_csv(paste0("C:\\Users\\internet",
  #                  "\\OneDrive - Bank Of Israel\\current_work",
  #                  "\\annual_report\\2022\\data",
  #                  "\\plots\\long_run_ipo_by_sector.csv"))

```


```{r plot_ipo_long_run_performance_by_year}

ret_df %>% 
  select(tase_id, year, contains("ret")) %>%
  pivot_longer(-c(tase_id, year),
               names_to = "adjustment") %>% 
  group_by(adjustment, year) %>% 
  summarise(avg = mean(value), med = median(value),
            .groups = "drop") %>% 
  pivot_longer(-c(adjustment,year)) %>% 
  ggplot(aes(x = year,
             y = value,
             fill = name)) + 
  geom_col(position = "dodge") + 
  facet_wrap(~adjustment, scales = "free") + 
  scale_y_continuous(labels = scales::percent_format()) +
  xlab(NULL) + ylab(NULL)


# ret_df %>% 
#   select(tase_id, year, contains("ret")) %>%
#   pivot_longer(-c(tase_id, year),
#                names_to = "adjustment") %>% 
#   group_by(adjustment, year) %>% 
#   summarise(avg = mean(value),
#             .groups = "drop") %>% 
#   pivot_wider(names_from = "adjustment",values_from = "avg") %>% 
#   write_csv(paste0("C:\\Users\\internet",
#                    "\\OneDrive - Bank Of Israel\\current_work",
#                    "\\annual_report\\2022\\data",
#                    "\\plots\\long_run_ipo_by_year.csv"))

  
  


```

