
```{r load_libraries}

library(tidyverse)

library(xts)

library(lubridate)

devtools::load_all()

# library(MiscImport)

```


```{r import_ta_125}

ta_125 = read_csv(paste0(Sys.getenv("USERPROFILE"),
                         "\\OneDrive - Bank Of Israel\\Data",
                         "\\TASE liquidity\\michael files",
                         "\\TA125.csv"),
                  show_col_types = FALSE) %>% 
  mutate(date = dmy(date))

```

```{r import_market_df}

market_df_filepath = paste0("C:\\Users\\internet",
                                "\\OneDrive - Bank Of Israel\\Data",
                                "\\TASE liquidity\\Rdata files",
                                "\\market_data_2022-12-12.rds")

market_df = import_boi_market_data(market_df_filepath) %>% 
  calculate_adjusted_price()

rm(market_df_filepath)

```


```{r import_ipo_list}

stocks_ipo = read_csv(paste0(Sys.getenv("USERPROFILE"),
                             "\\OneDrive - Bank Of Israel",
                             "\\Data\\TASE liquidity",
                             "\\michael files\\stocks_ipo.csv"),
                      show_col_types = FALSE) %>% 
  mutate(tase_id = as.character(tase_id))

stocks_ipo = stocks_ipo %>% 
  mutate(tase_id = recode(tase_id,
                          `456` = "259"))

ipo_trade_dur_df = market_df %>% 
  group_by(tase_id, sec_id) %>% 
  summarise(tibble(first_trade_year = year(min(date)),
                   trade_years = (max(date) - min(date)) %/% dyears(1)),
            .groups = "drop")

stocks_ipo = stocks_ipo %>% 
  left_join(ipo_trade_dur_df, by = "tase_id") %>% 
  arrange(tase_id) %>% 
  filter(!is.na(trade_years))



num_ipo = stocks_ipo %>% 
  count(tase_id, sort = TRUE)


stocks_ipo = stocks_ipo %>% 
  inner_join(num_ipo %>% 
               filter(n == 1) %>% 
               select(tase_id), by = "tase_id")

rm(ipo_trade_dur_df)

```

```{r cumulative_returns}

cum_ret_df = market_df %>% 
  select(tase_id, sec_id,date, close = close_adjusted) %>% 
  inner_join(stocks_ipo %>% 
               select(tase_id),by = "tase_id") %>% 
  left_join(ta_125 %>% 
              rename(index = ta_125), by = "date") %>% 
  group_by(tase_id, sec_id, date = as.yearmon(date)) %>% 
  summarise(across(c("close","index"),~mean(., na.rm = TRUE)),
            .groups = "drop") %>% 
  group_by(tase_id, sec_id) %>% 
  arrange(date) %>% 
  mutate(trade_periods = (date - date[1])) %>% 
  mutate(trade_periods = round(trade_periods,4)) %>%
  mutate(across(c("close","index"),
                .fns = list(log_ret = ~log(.) - log(.[1]),
                            simple_ret = ~ . /.[1] - 1))) %>% 
  # mutate(avg_ret = cum_ret / trade_periods) %>% 
  ungroup()

cum_ret_df = cum_ret_df %>% 
  select(-c("close","index")) %>% 
  pivot_longer(contains("ret"),names_to = "category") %>% 
   extract(category, into = c("source","ret_type"),
          regex = "^([^_]*)_(.*)") %>% 
  pivot_wider(names_from = source) %>% 
  mutate(index_adj = close - index) %>% 
  select(-index) %>% 
  pivot_longer(c("close","index_adj"),names_to = "adjustment_type")


```


# Desc stats


The sample contains `r nrow(num_ipo)` companies that performed
initial public offering on TASE. `r sum(num_ipo$n > 1)` of the
companies exited the market and came back later again performing an
IPO. For now this companies are excluded from the analysis.

## Attrition

```{r plot_attrition}

cum_ret_df %>% 
  count(trade_periods,name = "num_of_comps") %>% 
  ggplot(aes(trade_periods,num_of_comps)) + 
  geom_line() + 
  xlab(NULL) + ylab(NULL) + 
  ggtitle("Number of trading IPO companies (years since IPO)")



```


```{r ipo_trade_duration}

ggplot() + 
  geom_boxplot(data = stocks_ipo,
               aes(x = as.character(first_trade_year), y = trade_years)) + 
  geom_point(data = tibble(year = as.character(1993:2022),
                           floor = 2022 - 1993:2022),
             aes(x =  year, y = floor), color = "blue") +
  xlab(NULL) + ylab(NULL)




```


IPO companies exit the market quite quickly. The mean trading
periond is 'r round(mean(stocks_ipo$trade_years),2)' years
median trading perions is
'r round(median(stocks_ipo$trade_years),2)' years.

# Long run performance

In order to asses the long run performance of IPO's I calculate the buy and hold return 


```{r plot_cum_ret}

cum_ret_df  %>% 
  filter(trade_periods <= 10) %>%
  filter(ret_type == "simple_ret") %>% 
  group_by(trade_periods, adjustment_type) %>% 
  summarise(across(value,
                   .fns = list(mean = mean, median = median),
                   .names = "{.fn}"), .groups = "drop") %>% 
  pivot_longer(c("mean","median"), names_to = "summary_measure") %>% 
  mutate(adjustment_type = factor(adjustment_type,                                  labels = c("Absolute returns","Abnormal(index adjusted) returns"))) %>% 
  ggplot(aes(trade_periods, value, color = summary_measure)) + 
  geom_line() + 
  scale_y_continuous(labels = scales::percent_format()) + 
  facet_wrap(~adjustment_type, scales = "free") + 
  scale_x_continuous(breaks = seq(0,10,2)) +
  xlab("Years since IPO") + ylab(NULL) + 
  ggtitle("Cumulative returns since IPO")



```


```{r plot_ipo_long_run_performance_by_sector}

library(tidytext)


ret_df %>% 
  select(-year) %>%
  pivot_longer(-c(tase_id,sec_id,tase_sector, horizon),
               names_to = "adjustment") %>% 
  group_by(horizon,tase_sector,adjustment) %>% 
  summarise(avg = mean(value, na.rm = TRUE),
            med = median(value, na.rm = TRUE),
            .groups = "drop") %>% 
  filter(adjustment == "sec_ret_adj") %>%
  select(-adjustment) %>% 
  pivot_longer(-c(tase_sector, horizon)) %>% 
  ggplot(aes(x = value,
             y = reorder_within(tase_sector, value, horizon)),
             fill = name) + 
  geom_col(position = "dodge") + 
  facet_wrap(~horizon, scales = "free") + 
  scale_y_reordered() +
  scale_x_continuous(labels = scales::percent_format()) +
  xlab(NULL) + ylab(NULL)
  


# ret_df %>% 
#   select(contains("tase"), contains("ret")) %>%
#   pivot_longer(-c(tase_id,tase_sector),
#                names_to = "adjustment") %>% 
#   group_by(adjustment, tase_sector) %>% 
#   summarise(avg = mean(value),
#             .groups = "drop") %>% 
#   pivot_wider(names_from = adjustment, values_from = avg) %>% 
  # write_csv(paste0("C:\\Users\\internet",
  #                  "\\OneDrive - Bank Of Israel\\current_work",
  #                  "\\annual_report\\2022\\data",
  #                  "\\plots\\long_run_ipo_by_sector.csv"))

```


```{r plot_ipo_long_run_performance_by_year}

ret_df %>% 
  select(tase_id, year, contains("ret")) %>%
  pivot_longer(-c(tase_id, year),
               names_to = "adjustment") %>% 
  group_by(adjustment, year) %>% 
  summarise(avg = mean(value), med = median(value),
            .groups = "drop") %>% 
  pivot_longer(-c(adjustment,year)) %>% 
  ggplot(aes(x = year,
             y = value,
             fill = name)) + 
  geom_col(position = "dodge") + 
  facet_wrap(~adjustment, scales = "free") + 
  scale_y_continuous(labels = scales::percent_format()) +
  xlab(NULL) + ylab(NULL)


# ret_df %>% 
#   select(tase_id, year, contains("ret")) %>%
#   pivot_longer(-c(tase_id, year),
#                names_to = "adjustment") %>% 
#   group_by(adjustment, year) %>% 
#   summarise(avg = mean(value),
#             .groups = "drop") %>% 
#   pivot_wider(names_from = "adjustment",values_from = "avg") %>% 
#   write_csv(paste0("C:\\Users\\internet",
#                    "\\OneDrive - Bank Of Israel\\current_work",
#                    "\\annual_report\\2022\\data",
#                    "\\plots\\long_run_ipo_by_year.csv"))

  
  


```

