
```{r Import_wfe_data}

exchanges_list = read_csv(paste0(file.path(Sys.getenv("USERPROFILE"),
                                           fsep="\\"),
                                 "\\OneDrive - Bank Of Israel\\",
                                 "Data\\TASE liquidity\\",
                                 "OECD_Exchange_list.csv"))

wfe_df = read_csv(paste0(file.path(Sys.getenv("USERPROFILE"),
                                           fsep="\\"),
                         "\\OneDrive - Bank Of Israel",
                         "\\Data\\TASE liquidity\\WFE\\Stocks_Data.csv"))

wfe_df = wfe_df %>%
  rename_all(tolower) %>% 
  rename(indicator = `indicator name`) %>% 
  mutate_at(.vars = vars(value), as.numeric) %>% 
  filter(!is.na(value))

wfe_df = wfe_df %>% 
  filter(exchangename %in% exchanges_list$Exchange_1) %>% 
  mutate(indicator = str_remove_all(indicator,"Total Equity Market - "))

```



```{r balance_df}

balance_df = wfe_df %>% 
  filter(indicator %in% c(
    "Number of listed companies (Total)",
    "Number of delistings (Total)",
    "Number of new listings (Domestic Total) (Total)",
    "Number of new listings (Foreign Total) (Total)")) %>% 
  mutate(indicator = str_remove_all(indicator,"Number of ")) %>% 
  mutate(indicator = str_remove_all(indicator, " \\(Total\\)")) %>% 
  mutate(indicator = str_replace_all(indicator,pattern = "\\s","_")) %>% 
  pivot_wider(id_cols = c(indicator,year,exchangename),
              names_from = indicator,values_from = value) %>% 
  mutate(new_listings = `new_listings_(Domestic_Total)` + 
           `new_listings_(Foreign_Total)`) %>% 
  select(-`new_listings_(Domestic_Total)`,-`new_listings_(Foreign_Total)`) 
  
  
  # Calculate changes in comps
  
  balance_df = balance_df %>% 
  group_by(exchangename) %>% 
  arrange(year) %>% 
  mutate(listed_change = c(NA, diff(listed_companies))) %>% 
  mutate(issue_change = new_listings - delistings) %>% 
  ungroup()

```


\subsection{Delistings}


```{r delisting_comps_by_year}

ggplot(balance_df %>% 
         group_by(year) %>% 
         summarise(delistings_share = sum(delistings, na.rm = TRUE) /
                     sum(listed_companies, na.rm = TRUE)),
       aes(x = as.character(year), y = delistings_share)) + 
  geom_col() + 
  labs(x = "", y = "", title = "Share of delisting \n (OECD average)") + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 90, vjust = 0.5))

```

Delisting activity peak is at 2007-2011 probably reflects both the Global Financial Crises and Europe's sovereign debt crises.


```{r delisting_comps_by_comp}

ggplot(balance_df %>% 
         group_by(exchangename, year) %>% 
         summarise(delistings_share = delistings / listed_companies,
                   .groups = "drop") %>% 
         group_by(exchangename) %>% 
         summarise(avg_delist_share = mean(delistings_share, na.rm = TRUE),
                   .groups = "drop") %>% 
         filter(complete.cases(.)) %>% 
         filter(is.finite(avg_delist_share)),
       aes(x = reorder(exchangename,avg_delist_share), y = avg_delist_share,
           fill = if_else(exchangename == "Tel-Aviv Stock Exchange",
                          "Israel", "Other"))) + 
  geom_col() + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("Israel" = "lightblue", "Other" = "lightgrey")) + 
  coord_flip() + 
  labs(x = "", y = "", title = "Share of delisting \n (2000- 2020 average)") + 
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(legend.position = "none")

```

Israel is characterized by relatively low delisting rate (lower third) among OECD exchanges
 
\subsection{Issues}


```{r listed_comps_by_year}

ggplot(balance_df %>% 
         group_by(year) %>% 
         summarise(new_listings_share = sum(new_listings, na.rm = TRUE) /
                     sum(listed_companies, na.rm = TRUE)) %>% 
         filter(is.finite(new_listings_share)),
       aes(x = as.character(year), y = new_listings_share)) + 
  geom_col() + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
  labs(x = "", y = "", title = "Share of new listings \n (OECD average)") + 
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 90, vjust = 0.5))

```


```{r issued_comps_by_comp}

ggplot(balance_df %>% 
         group_by(exchangename, year) %>% 
         summarise(new_listings_share = new_listings / listed_companies,
                   .groups = "drop") %>% 
         group_by(exchangename) %>% 
         summarise(avg_new_listings_share = mean(new_listings_share,
                                                 na.rm = TRUE),
                   .groups = "drop") %>% 
         filter(complete.cases(.)) %>% 
         filter(is.finite(avg_new_listings_share)),
       aes(x = reorder(exchangename,avg_new_listings_share),
           y = avg_new_listings_share,
           fill = if_else(exchangename == "Tel-Aviv Stock Exchange",
                          "Israel", "Other"))) + 
  geom_col() + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
  scale_fill_manual(values = c("Israel" = "lightblue", "Other" = "lightgrey")) + 
  coord_flip() + 
  labs(x = "", y = "", title = "Share of new listings \n (2000- 2020 average)") + 
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(legend.position = "none")

```

Similar to delisting activity Israel's issuance activity seems to be relatively low (lower third) among OECD exchanges

\subsection{Trading activity}

```{r trading_df}

trading_df = wfe_df %>% 
  select(-region, -currencyname, -ytd) %>% 
  filter(indicator %in% c("Number of shares traded (Total)",
                          "Number of trading days",
                          "Number of trades (EOB)",
                          "Market Capitalisation",
                          "Value traded (EOB Total)",
                          "Number of trading participants"))

```

```{r plot_trading_by_exchange}

ggplot(trading_df %>% 
         filter(indicator == "Number of trading days") %>% 
         group_by(exchangename, indicator) %>% 
         summarise(avg_val = mean(value, na.rm = TRUE), .groups = "drop") %>%
         filter(complete.cases(.)),
       aes(x = reorder(exchangename, avg_val), y = avg_val)) + 
  geom_col() + 
  labs(x = "", y = "", title = "") + 
  coord_flip() + 
  theme_bw()

```

