---
title: "TASE companies evolution"
output: pdf_document
---

```{r setup, include=FALSE,}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

```


```{r Load_libraries}

library(devtools)

library(tidyverse)

library(xts)

library(stargazer)

library(readxl)

load_all()

```


```{r Import_data}

status_df = import.TASE.comps_status()

tase = inner_join(read.csv(paste0(file.path(Sys.getenv("USERPROFILE"),"Documents",
                 fsep="\\"),"\\Data\\TASE\\TA_35_2000_2019.csv"),
                stringsAsFactors = FALSE) %>% 
  setNames(c("Date","Basis","Open","Close","High","Low","Market_Cap")) %>% 
  mutate(Date = as.Date(Date, format = "%d/%m/%Y")) %>% 
  select(Date,Close) %>% 
  group_by(Year = format(Date,"%Y")) %>% 
  summarise(Avg_Close_35 = mean(Close)),
  read.csv(paste0(file.path(Sys.getenv("USERPROFILE"),"Documents",
                 fsep="\\"),"\\Data\\TASE\\TA_125_2000_2019.csv"),
                stringsAsFactors = FALSE) %>% 
  setNames(c("Date","Basis","Open","Close","High","Low","Market_Cap")) %>% 
  mutate(Date = as.Date(Date, format = "%d/%m/%Y")) %>% 
  select(Date,Close) %>% 
  group_by(Year = format(Date,"%Y")) %>% 
  summarise(Avg_Close_125 = mean(Close)))

```


```{r plot_comps_evolution}

comps_evolution_plot = ggplot(status_df %>% 
                                filter(Sector == "Total"),
                              aes(x = Year, y = End_Year, group = 1)) + 
  geom_col(width = 0.7) + 
  geom_text(aes(x = Year, y = End_Year, label = End_Year), vjust = -1,
            color = "magenta", size = 3) + 
  labs(x = "", y = "", title = "Number of listed companies in TASE") + 
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90))

y_range = ggplot_build(comps_evolution_plot)$layout$panel_params[[1]]$y.range

y_range[2] = 1.05 * y_range[2]

print(comps_evolution_plot + 
        ylim(y_range))

rm(y_range)

```

Number of listed companies has been declining since it peaked at 2007-2008, there are currently 
`r status_df$End_Year[status_df$Sector == "Total" & status_df$Year == max(status_df$Year)]` listed
on the exchange.The average number has been `r mean(status_df$End_Year[status_df$Sector == "Total"])`
companies.

```{r plot_net_new_comps_evolution}

ggplot(status_df %>% 
  filter(Sector == "Total") %>% 
  select(Year, Issued_Comps, Delisted_Comps) %>% 
  mutate(Net_New_Comps = Issued_Comps - Delisted_Comps) %>% 
  mutate(Delisted_Comps = -1 * Delisted_Comps) %>% 
  gather(key = Indicator, value = Comps_Num, -Year,-Net_New_Comps)) + 
  geom_col(aes(x = Year, y = Comps_Num, fill = Indicator)) +
  geom_line(aes(x = Year,group = 1, y = Net_New_Comps, color = "Net new comps")) + 
  scale_color_manual(values = "black") + 
  # geom_hline(yintercept = 0, linetype = "dashed") + 
  labs(x = "", y = "") + 
  theme_bw() + 
  theme(legend.position = "bottom",legend.title = element_blank(),
        axis.text.x = element_text(angle = 90))

```


```{r plot_comps_evolution_by_sectype}

ggplot(status_df %>% 
  filter(Sector %in% c("Total Shares","Total Bonds")),
  aes(x = Year, y = End_Year, group = Sector, fill = Sector)) + 
  geom_col(position = "dodge") + 
  labs(x = "", y = "", title = "Number of listed companies in TASE") + 
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom",
        axis.text.x = element_text(angle = 90))

```


```{r plot_comps_evolution_by_sector}

ggplot(status_df %>% 
  filter(!Sector %in% grep("Total",unique(Sector),value = TRUE)),
  aes(x = Year, y = End_Year, group = Sector, fill = Sector, label = End_Year)) + 
  geom_bar(stat = "identity") + 
  # geom_text(size = 3, position = position_stack(vjust = 0.5)) + 
  scale_fill_brewer(type = "div", palette = "Spectral") + 
  labs(x = "", y = "", title = "Number of listed companies in TASE \n (by sector)") + 
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom",
        axis.text.x = element_text(angle = 90), legend.title = element_blank())

```

A study of sector evolution reveals that the most prominent and stable sectors are: industry,
real estate, services and holdings. However in the last 5 years holding's and service's share
decreased significantly while new sectors such as technology and biomed entered the stage.


\subsection{Delisting companies}

```{r plot_delisting_comps}

delisted_comps_plot = ggplot(status_df %>% 
                               filter(Sector == "Total"),
                             aes(x = Year, y = Delisted_Comps, label = Delisted_Comps)) + 
  geom_col(width = 0.7) + 
  geom_text(aes(x = Year, y = Delisted_Comps), vjust = -1,
            color = "magenta", size = 3) + 
  labs(x = "", y = "", title = "Number of delisted companies") + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 90), plot.title = element_text(hjust = 0.5))

y_range = ggplot_build(delisted_comps_plot)$layout$panel_params[[1]]$y.range

y_range[2] = 1.02 * y_range[2]

print(delisted_comps_plot + 
        ylim(y_range))

rm(y_range)

```

A total of `r sum(status_df$Delisted_Comps[status_df$Sector == "Total"])` (`r sum(status_df$Delisted_Comps[status_df$Sector == "Total Shares"])` shares and `r sum(status_df$Delisted_Comps[status_df$Sector == "Total Bonds"])` bonds) companies were delisted from TASE during the entire period.

```{r calculate_delisting_cor}

temp_df = status_df %>% 
  filter(Sector == "Total") %>% 
  select(Year, Delisted_Comps) %>% 
  inner_join(tase[,c("Year","Avg_Close_125")])


del_cor = cor(diff(temp_df$Delisted_Comps),diff(temp_df$Avg_Close_125))

rm(temp_df)

```


We can see that the peak in delisting companies took place in 2012-2014 period, 2018 was also a year with significant delisting activity. The delisting activity seems to take place during market drops (the correlation between TA 125 and delisting companies is `r round(del_cor,2)`)
