---
title: "Work outline"
header-includes:
   - \usepackage{xcolor}
output: pdf_document
---

```{r setup, include=FALSE,}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

```


```{r Load_libraries}

library(devtools)

library(tidyverse)

library(xts)

library(stargazer)

load_all()

```


```{r Import_data}

var_list = read_csv(paste0(Sys.getenv("USERPROFILE"),
                           "\\OneDrive - Bank Of Israel\\Data",
                           "\\TASE liquidity\\michael files",
                           "\\Variables_List.csv"), show_col_types = FALSE)


df = read_rds(paste0(Sys.getenv("USERPROFILE"),
                     "\\OneDrive - Bank Of Israel\\Data",
                     "\\TASE liquidity\\Rdata files\\final_df.RDS")) %>% 
  rename_all(tolower)

df = df %>% 
  mutate(capex_to_revenue = capex_cashflow / revenue) %>%
  mutate(roa = operating_profit / total_assets) %>%
  mutate(mb = market_cap / total_assets) %>% 
  rename(size = market_cap_log) %>% 
  select(tase_id, date, any_of(na.omit(var_list$df_varname)))


```



\section{Introduction}

The purpose of the work is to identify the reasons
of firm's delistings from trade. The method is a logit regression that evaluates firm's characteristics in a sample
that consists of delisted firms and matched trading firms.

\section{Empirical specification}

\begin{align*}
	Pr(Delisting)  = \alpha & + \beta_{1} Leverage + \beta_{2} MB  
	                          + \beta_{3} CAPEX  + \beta_{4}ROA\\ 
	                        & + \beta{5} FreeCashFlow 
	                          + \beta_{6} InsiderOwnership \\
                          & + \beta_{7} Size + \beta_{8} TradeVolume 
                            + \beta_{9} Illiqudity
\end{align*}

Where:

\begin{itemize}
  \item
  \textcolor{red}{InsiderOwnership - currently using Public share (1-free float),
  maybe try your algorithm controlling shareholder data?}

\end{itemize}


\section{Descriptive Stats}

\subsection{Financial reports and market data}


This data set was constructed by complementing the initial data set (data that was gathered in previous work) with data from BOI (MOS) database. The data time period is `r paste0(range(df$Date), collapse = "-")` at quarterly frequency. The data set is not balanced, the issue seems to be with market variables (Public Share, Turnover and Market Cap).



```{r df_stat,results='asis'}

stargazer(df, header = FALSE,
          omit.summary.stat = c("p25","p75"), digits = 2)

```

\subsection{TASE companies status data}


```{r Import_tase_comps_list}

tase_comps_list = read_csv(paste0(Sys.getenv("USERPROFILE"),
                                  "\\OneDrive - Bank Of Israel",
                                  "\\Data\\TASE liquidity",
                                  "\\TASE Comps list_revised.csv"),
                           show_col_types = FALSE)

tase_comps_list = tase_comps_list %>% 
  mutate(Delisting_Date_coalesce = coalesce(Delisting_Date_old, Delisting_Date)) %>% 
  select(-Delisting_Date_old, Delisting_Date)


delisted_comps = tase_comps_list %>% 
  filter(Delisted == 1) %>% 
  nrow()

delisted_dates = tase_comps_list %>% 
  filter(Delisted == 1) %>% 
  filter(!is.na(Delisting_Date)) %>% 
  nrow()

```


```{r import_boi_delisting_data}

boi_delisted_comps = read_



```


The data set includes  TASE companies. We have data on the company status (delisted or nor), the date when the company was delisted and the reason for delisting. There are a total of `r nrow(tase_comps_list)` companies with `r delisted_comps` of them were delisted\footnote{According to TASE reports there were 576 delisted shares}. We have a delisting date for only `r delisted_dates` of the companies (delisting dates start from is `r as.yearqtr(min(tase_comps_list$Delisting_Date, na.rm = TRUE))`).

There is another data set (from your previous work) that has delisting dates for
`r sum(!is.na(tase_comps_list$Delisting_Date_old))` (19 of them identified by name only) and perhaps can be used to complement the main data set but the delisting dates are quite different (few quarters some times few years). \textcolor{red}{Need to decide whether verify (case by case) or go on with using one of the data sets}

<!-- \section{Results} -->

<!-- \section{Appendix} -->

```{r ,child="Appendix.Rmd", eval = FALSE}

```

