---
title: "Work outline"
header-includes:
   - \usepackage{xcolor}
output: pdf_document
---

```{r setup, include=FALSE,}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

```


```{r Load_libraries}

library(devtools)

library(tidyverse)

library(xts)

library(stargazer)

load_all()

```


```{r Set_parameters}

x_vars = c("Illiq","Market_Cap_log","Turnover_log","Public_Share","HHI","IPO",
           "Total_Assets","Operating_Profit","Revenue","Net_Profit","Equity",
           "Total_Liabilities","Leverage")

```


```{r Import_data}

df = read_rds(paste0(file.path(Sys.getenv("USERPROFILE"),fsep="\\"),
                     "\\OneDrive - Bank Of Israel\\Data\\TASE",
                     " liquidity\\final_df.RDS"))

df = df %>% 
  select(Date, any_of(x_vars)) %>% 
  mutate_if(is.numeric,.funs = ~ifelse(abs(.) == Inf,NA,.))


```


```{r Import_market_data, eval=FALSE}

if(file.exists(paste0(file.path(Sys.getenv("USERPROFILE"),fsep="\\"),
                      "\\OneDrive - Bank Of Israel\\Data\\",
                      "TASE liquidity\\market_df.RDS"))){
  
  market_df = read_rds(paste0(file.path(Sys.getenv("USERPROFILE"),fsep="\\"),
                      "\\OneDrive - Bank Of Israel\\Data\\",
                      "TASE liquidity\\market_df.RDS"))
  

} else {
  
  market_df = read_rds(paste0("C:\\Users\\internet\\Documents\\Data\\TASE\\Market Data",
                          "\\Market_data_stocks_2001-2019.Rds")) %>% 
    get.market.variables()
  
}


```


```{r Import_finrep_data, eval=FALSE}

if(file.exists(paste0(file.path(Sys.getenv("USERPROFILE"),fsep="\\"),
                      "\\OneDrive - Bank Of Israel\\Data\\",
                      "TASE liquidity\\finrep_df.RDS"))){
  
  finrep_df = read_rds(paste0(file.path(Sys.getenv("USERPROFILE"),fsep="\\"),
                      "\\OneDrive - Bank Of Israel\\Data\\",
                      "TASE liquidity\\finrep_df.RDS"))
  
} else {
  
  finrep_df = import.boi.finrep.data() %>% 
  mutate_if(((!names(.) %in% c("Date","TASE_branch","TASE_ID")) & !is.numeric(.)),
            as.numeric) %>% 
  select(Date, TASE_ID, TASE_branch, Operating_Profit,Net_Profit,
         Equity,Revenue,Total_Assets, Total_Liabilities, Capex_CashFlow,
         Operating_CashFlow) %>% 
  mutate(Capex_to_revenue = Capex_CashFlow / Revenue) %>% 
  mutate(ROA = Operating_Profit / Total_Assets) %>% 
  mutate(Free_CashFlow = Operating_CashFlow / Total_Assets)
  
  
}

```


```{r process_data, eval=FALSE}

df = full_join(finrep_df, market_df, by = c("Date" = "Date",
                                            "TASE_ID" = "Comp_ID"))

df = df %>% 
  mutate(MB = Market_Cap / Equity) %>% 
  mutate(Market_Cap_log = log(Market_Cap)) %>% 
  mutate(Turnover_log = log(Turnover)) %>% 
  mutate(Leverage = Total_Liabilities / Total_Assets)


rm(finrep_df, market_df)

```


```{r import_old_data, eval=FALSE}

old_df = import.old.regression.data()

merged_df = full_join(df,old_df[,names(old_df)[names(old_df) %in% names(df)]],
                      by = c("Date","TASE_ID"), suffix = c("_new","_old")) 

final_df = merged_df

for(varname in grep("_new$",names(final_df),value = TRUE)){
  
  main_var = sym(varname)
  
  backup_var = sym(str_replace(varname,"new","old"))
  
  final_df = final_df %>% 
    mutate(!!varname := coalesce(!!main_var,!!backup_var))
  
  rm(main_var, backup_var)

}

final_df = final_df %>% 
  select(-ends_with("_old")) %>% 
  rename_at(.vars = vars(ends_with("_new")),.funs = list(~str_remove(.,"_new")))
  

# Test for data completness

# if(length(x_vars[!x_vars %in% names(final_df)]) > 0){
#   
#   message(paste("The following variables are missing:",
#                 paste0(x_vars[!x_vars %in% names(df)],
#                        collapse = ",")))
#   
# }
# 

```


\section{Introduction}

The purpose of the work is to identify the reasons
of firm's delistings from trade. The method is a logit regression that evaluates firm's characteristics in a sample
that consists of delisted firms and matched trading firms.

\section{Empirical specification}

\begin{align*}
	Pr(Delisting)  = \alpha & + \beta_{1} Leverage + \beta_{2} MB  
	                          + \beta_{3} CAPEX  + \beta_{4}ROA\\ 
	                        & + \beta{5} FreeCashFlow 
	                          + \beta_{6} InsiderOwnership \\
                          & + \beta_{7} Size + \beta_{8} TradeVolume 
                            + \beta_{9} Illiqudity
\end{align*}

Where:

\begin{itemize}
  \item
  \textcolor{red}{InsiderOwnership - currently using }

\end{itemize}


\section{Descriptive Stats}

\subsection{Financial reports and market data}

This dataset was constructed by complementing the initial dataset (data that was gather in previous work) with data form BOI (MOS) database. The data time period is `r paste0(range(df$Date), collapse = "-")` at quarterly frequency. The dataset is not balanced, the issue seems to be with market variables (Public Share, Turnover and Market Cap).


```{r df_stat,results='asis'}

stargazer(df, header = FALSE,
          omit.summary.stat = c("p25","p75"), digits = 2)

```

\subsection{TASE companies status data}


```{r Import_tase_comps_list}

tase_comps_list = read.csv(paste0(file.path(Sys.getenv("USERPROFILE"),
                                            fsep="\\"),
                                  "\\OneDrive - Bank Of Israel\\Data",
                                  "\\TASE liquidity\\TASE Comps list.csv"),
                           stringsAsFactors = FALSE)

tase_comps_list = tase_comps_list %>% 
  rename(TASE_ID = 1) %>% 
  mutate(Delisting_date = parse_date(Delisting_date,format = "%d%.%m%.%Y"))


delisted_comps = sum(tase_comps_list$Delisted)

delisted_dates = sum(!is.na(tase_comps_list$Delisting_date))

```

The data set includes  TASE companies. We have data on the company status (delisted or nor), the date when the company was delisted and the reason for delisting. The dataset is incomplete : there are a total of `r nrow(tase_comps_list)` companies, `r delisted_comps` of them were delisted. We have a delisting date for `r delisted_dates` of the companies.



\section{Results}

\section{Appendix}

```{r ,child="Appendix.Rmd", eval = FALSE}

```

