---
title: "Work outline"
header-includes:
   - \usepackage{xcolor}
output: pdf_document
---

```{r setup, include=FALSE,}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

```


```{r Load_libraries}

library(devtools)

library(tidyverse)

library(xts)

library(stargazer)

load_all()

```



```{r Import_data}

del_comps_filepath = paste0("C:\\Users\\internet",
                            "\\OneDrive - Bank Of Israel",
                            "\\Data\\TASE liquidity",
                            "\\michael files\\delisted_comps.csv")

ipo_filepath = paste0("C:\\Users\\internet",
                            "\\OneDrive - Bank Of Israel",
                            "\\Data\\TASE liquidity",
                            "\\michael files\\ipo_dates.csv")

comps_dates = import_comps_dates_and_status(ipo_filepath,
                                            del_comps_filepath) %>% 
  filter(!tase_id %in% c("1286","1701"))


df = read_rds(paste0("C:\\Users\\internet",
                     "\\OneDrive - Bank Of Israel\\Data",
                     "\\TASE liquidity\\Rdata files",
                     "\\final_df_2022-11-20.rds"))


matched_df = get_matched_df(df, comps_dates,
                            matching_variable = "size",
                            threshold = 0.15)
  
  
rm(del_comps_filepath, ipo_filepath)


```



\section{Introduction}

The purpose of the work is to identify the reasons
of firm's delistings from trade. The method is a logit regression that evaluates firm's characteristics in a sample
that consists of delisted firms and matched trading firms.

\section{Empirical specification}

\begin{align*}
	Pr(Delisting)  = \alpha & + \beta_{1} Leverage + \beta_{2} MB  
	                          + \beta_{3} CAPEX  + \beta_{4}ROA\\ 
	                        & + \beta{5} FreeCashFlow 
	                          + \beta_{6} InsiderOwnership \\
                          & + \beta_{7} Size + \beta_{8} TradeVolume 
                            + \beta_{9} Illiqudity
\end{align*}

Where:

\begin{itemize}
  \item
  \textcolor{red}{InsiderOwnership - currently using Public share (1-free float),
  maybe try your algorithm controlling shareholder data?}

\end{itemize}


\section{Descriptive Stats}

\section{Univariate analysis}

```{r}

matched_df %>% 
  group_by(tase_id) %>%
  mutate(step = time_period - min(time_period)) %>% 
  ungroup() %>% 
  select(-time_period, -tase_id) %>% 
  group_by(comp_type, step) %>% 
  summarise(across(everything(), ~median(.,na.rm = TRUE)),
            .groups = "drop") %>% 
  pivot_longer(-c(comp_type, step)) %>% 
  ggplot(aes(step, value, color = comp_type)) + 
  geom_line() + 
  facet_wrap(~name, scales = "free")


```

